Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-20 scenarios/cdsr/trunk/papers/AAAI2012/qsr-extraction.tex
minor edits

JK working on this!

%Given data from Dora's spatial model, we compute the following qualitative spatial representations. First, we extract the object and room entities from the sensor data. Next, we determine the qualitative spatial relationships between these entities. For the room, we compute its region as a convex hull around the set of points. For the objects, we consider only their centroids. For each pair of adjacent objects, we compute topological and positional relationships. Adjacency is determined by creating a voronoi diagram as is standard geometric reasoning \cite{Forbus/etal2003}. For the topological relationships, we use the region connection calculus, RCC8, \cite{Cohn:2001}. For positional relations, we use two predicates \fw{leftOf} and \fw{below}. An entity is \fw{leftOf} another if the x coordinate of its centroid is less than that of the other entity's. An entity is \fw{below} another if the y coordinate of its centroid is less than that of the other entity's. Objects whose x or y coordinates are within a threshold of one another will not be related by \fw{leftOf} or \fw{below} positional relations.

>>>>

For each object that Dora detects we compute 8 spatial relations between that object and each of the objects adjacent to it; adjacency is determined using a voronoi diagram, as is standard in geometric reasoning \cite{Forbus/etal2003}. The relations we compute between each given \emph{landmark} object and its adjacent neighbour are analogous to the cardinal and intermediate points on the compass when the compass is centered on the object. The canonical directions of these relations are defined using the following vectors: $<0,1>$, $<1,1>$, $<1,0>$, $<1,-1>$, $<0,-1>$, $<-1,-1>$, $<-1,0>$, $<-1,1>$.

We generate these relations as follows. Taking each object in the room in turn to be the current landmark, we translate the origin of the room to the landmark's centroid. This results in the coordinates of the all the other objects in the room being translated into a frame of reference whose origin is the centroid of the landmark.  For each neighbour object adjacent to the landmark we compute the 8 relations by calculating the inner angle between the vector from the origin (the landmark's centroid) and the neighbour's location and the direction vector of the relation, as defined above. This angle is computed by taking the dot product of these two vectors. $\dots$
